\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm,bm,graphicx,color,epsfig}

\addtolength{\textwidth}{1in}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textheight}{1.6in}
\addtolength{\topmargin}{-0.8in}

% formatting
\parindent = 0 pt
\parskip = 4 pt

\title{CurveLab Toolbox, Version 2.1.3}
\author{Emmanuel Cand\`{e}s, Laurent Demanet,  Lexing Ying
}

\date{}
\begin{document}

\maketitle
%------------------------------------------
\section{Introduction}
CurveLab is a collection of Matlab and C++ programs for the {\em Fast
Discrete Curvelet Transform} in two and three dimensions.

For the 2d curvelet transform, the software package includes two
distinct implementations: the wrapping-based transform and the
transform using unequally-spaced fast Fourier transform (USFFT). Both
variants are based on the Curvelet transform as described in `New
Tight Frames of Curvelets and Optimal Representations of Objects with
Piecewise $C^2$ Singularities', {\it Comm. Pure Appl. Math.}  {\bf 57}
(2004) 219-266. The implementation is also discussed in detail in
`Fast Discrete Curvelet Transforms', {\it Multiscale Model. Simul.}
{\bf 5} (2006), no. 3, 861-899. We
advise users to become familiar with these references.

The two implementations differ by the choice of spatial grid used to
translate curvelets at each scale and angle.
\begin{itemize}
\item The USFFT version uses a decimated rectangular grid tilted along
  the main direction of each curvelet. There is one such grid per
  scale and angle, and this implementation is therefore very close to
  the definition given in the above reference. For the digital
  transform, tilting the grids induces a resampling of the Fourier
  transform on semi-regular grids, hence the use of a (perhaps novel)
  USFFT routine. For the inversion, a conjugate-gradient solver
  rapidly converges to the solution.
\item The wrapping version uses, instead, a decimated rectangular grid
  aligned with the image axes. For a given scale, there are
  essentially two such grids (decimated mostly horizontally or mostly
  vertically). The resulting sampling is not as faithful to the
  original transform, but the basis functions are curvelets as much as
  in the USFFT-based implementation. Since no interpolation is
  necessary in the frequency plane, the transform is a numerical
  isometry and can be inverted by its adjoint.
\end{itemize}

For the 3d curvelet transform, the software in this package is an
extension of the wrapping version in 2d. Due to the large size of the
3d data and the increasing redundancy of the curvelet transform, three
different implementation are included:
\begin{itemize}
\item The in-core implementation which stores both the input data and
  the curvelet coefficients in the memory (suitable for small size data
  set).
\item The out-core implementation which stores the input data in the
  memory and most of the curvelet coefficients on the disc (suitable
  for medium size data set).
\item The MPI-based parallel implementation which distributes both
  input data and the curvelet coefficients on multiple nodes. The
  parallel implementation can successfully handle input data of size $1k
  \times 1k \times 1k$.
\end{itemize}

The C++ part of the package includes all the 2d and 3d implementations
listed above. The Matlab part of this package includes only the 2d
implementations of the USFFT and wrapping transforms.

%------------------------------------------
\section{Installation}
Copy the CurveLab package into the directory of your choice, and 
expand it with
\begin{verbatim}
  gunzip CurveLab-2.0.tar.gz
  tar xvf CurveLab-2.0.tar
\end{verbatim}

\paragraph{Matlab part.} The Matlab implementation for the wrapping-based transform can be
found in the directory \verb=fdct_wrapping_matlab=, while the Matlab
implementation for the USFFT-based transform is in the directory
\verb=fdct_usfft_matlab=. In both directories, you can find several
demos which explain how to use the software. Before running the demos
in the directory \verb=fdct_usfft_matlab=, run
\verb=fdct_usfft_path.m= to set the correct searching path.

\paragraph{C++ part.} The C++ implementation is tested on Unix-type 
platforms, including Linux, SunOS and MacOS. The installation requires
g++ (version 3.2 or 3.3), and Matlab's mex compiler (version 13 or 14)
if you want to compile the mex files for the C++ implementation (make
sure the mex compiler use the same version of g++).

To install the C++ implementations (except the MPI-based parallel 3d
transform)
\begin{itemize}
\item
  Download and install FFTW version 2.1.5 (\verb=http://www.fftw.org=).
  Make sure to type \verb=./configure --with-pic= when configure FFTW.
\item
  In makefile.opt, \newline
  set \verb=FFTW_DIR= to be the path in which FFTW 2.1.5 is installed, and \newline
  set \verb=MEX= to be the correct mex compiler (optional).
\item
  While in the main toolbox directory, type \newline
  \verb=make lib= to build the libraries for both the wrapping-based and the USFFT-based implementations \newline
  \verb=make test= to test the C++ installation (optional) \newline
  \verb=make matlab= to generate the mex files of the C++ implementation, which can be called in Matlab (optional)
\end{itemize}

For the 2d implementations, the source files of the ``C++ wrapping
version'' are in the directory \verb=fdct_wrapping_cpp/src=, while the
mex files generated by \verb=make matlab= and the demo files are in
the directory \verb=fdct_wrapping_cpp/mex=. The source files of the
``C++ USFFT version'' are in the directory \verb=fdct_usfft_cpp/src=,
while the mex files and the demo files are in the directory
\verb=fdct_usfft_cpp/mex=.

For the 3d implementations, the source files for the in-core version
are in the directory \verb=fdct3d/src=, while the mex files (generated
by \verb=make matlab= and the Matlab demo files are in the
directory \verb=fdct3d/mex=. The source files of the out-core version
are in the directory \verb=fdct3d_outcore=.

To install the MPI-based parallel 3d implementation, please read
\verb=fdct3d_mpi/src/README= for details.

%------------------------------------------
\section{List of Matlab Files}

The 2d Matlab implementations of the wrapping-based and USFFT-based
transforms are in the directories \verb=fdct_wrapping_matlab= and
\verb=fdct_usfft_matlab= respectively. The Matlab interface of the C++
implementations is located in the directories
\verb=fdct_wrapping_cpp/mex= and \verb=fdct_usfft_cpp/mex=. Below is a
(non-exhaustive) list of the \verb=.m= files which can be found in
those directories. \verb=xxx= stands for either \verb=wrapping= or
\verb=usfft=.

\paragraph{Basic transform functions.}
\begin{itemize}
\item  \verb=fdct_xxx.m= -- forward curvelet transform.
\item  \verb=ifdct_xxx.m= -- inverse curvelet transform.
\item  \verb=afdct_xxx.m= -- adjoint curvelet transform (only for
  USFFT-based transform since for the wrapping transform, the adjoint 
  is the same as the inverse transform).
\item \verb=fdct_xxx_param.m= -- this function returns the location of
  each curvelet in phase-space.
\end{itemize}

\paragraph{Useful Tools.}
\begin{itemize}
\item  \verb=fdct_xxx_dispcoef.m= -- a function which returns a matrix
  containing all the curvelet coefficients.
\item  \verb=fdct_xxx_pos2idx.m= -- for a fixed scale and a fixed
  direction, this function returns the index of the curvelet closest
  to a certain point in the image.
\end{itemize}

\paragraph{Demo Files.}
\begin{itemize}
\item  \verb=fdct_xxx_demo_basic.m= -- displays a curvelet in the spatial and frequency domain.
\item  \verb=fdct_xxx_demo_recon.m= -- partial reconstruction using the curvelet transform.
\item  \verb=fdct_xxx_demo_disp.m= -- displays all the curvelet coefficients of an image.
\item  \verb=fdct_xxx_demo_denoise.m= -- image denoising via curvelet shrinkage.
\end{itemize}

There are two extra Matlab demos in \verb=fdct_wrapping_matlab= directory:
\begin{itemize}
\item \verb=fdct_wrapping_demo_denoise_enhanced.m= -- further techniques for image denoising.
\item \verb=fdct_wrapping_demo_wave.m= -- wave propagation using curvelets.
\end{itemize}

An extra file \verb=fdct_usfft_path.m= is included in
\verb=fdct_usfft_matlab= directory. This script needs to be called to
append several subdirectories into the searching path.

The Matlab code for the in-core 3d transform are located in
\verb=fdct3d/mex=. Below is a list of the \verb=.m= files.

\paragraph{Basic transform functions.}
\begin{itemize}
\item  \verb=fdct3d_forward.m= -- forward 3d curvelet transform.
\item  \verb=fdct3d_inverse.m= -- inverse 3d curvelet transform.
\item  \verb=fdct3d_param.m= -- a function which returns the location
  of each curvelet in phase-space.
\end{itemize}

\paragraph{Demo Files}
\begin{itemize}
\item  \verb=fdct3d_demo_basic.m= -- displays a curvelet in the spatial and frequency domain.
\end{itemize}

Extra information for each of these functions can be obtained by
typing (at the Matlab prompt) \verb=help= followed by the name of the
function.

%------------------------------------------
\section{Changes}
\begin{itemize}
\item Fixed bug in the 2d C++ implementation for input data with odd
  size.
\item In 2d C++ implementation, changed the input data structure from
  class \verb=CpxOffMat= to class \verb=CpxNumMat=. The test files are
  changed accordingly.
\item The mirror-extended curvelet frame has been proposed in
  technical report `Curvelets and Wave Atoms for Mirror-Extended
  Images' by L. Demanet and L. Ying. The implementation is
  in the subdirectory \verb=mecv=.
\end{itemize}

%------------------------------------------
\section{Copyright and Contact}
CurveLab is copyright \copyright $\,$ California Institute of
Technology, 2005-2007. For further information, please contact
\verb=curvelab@curvelet.org=.

\end{document}
